Human Judgement Forecasting of COVID-19 in the UK

### 2023-03-29 manuscript/manuscript.tex

The median number of unique participants in any given week was 17, the minimum was 6 and the maximum was 51. This was higher than the number of participants in \cite{bosseComparingHumanModelbased2022} (which had a median number of 6, a minimum of 2, and a maximum 10). With respect to the number of submissions from an individual participant, we observed similar patterns as \cite{bosseComparingHumanModelbased2022}: An individual forecaster participated on average in 2.6 weeks out of 13. The median number of submissions from a single individual was one, meaning that similar to \citep{bosseComparingHumanModelbased2022} most forecasters dropped out after their first submission. Only five participants submitted a forecast in ten or more weeks and only two submitted a forecast in all thirteen weeks, one of whom is an author on this study. The number of direct forecasts (median: 13 for cases and 12 for deaths) was higher than the number of $R_t$ forecasts (median: 6 for both cases and deaths) in all weeks (see Figure \ref{fig:num-forecasters}).

@@

A comparison of "experts" and "non-experts" (self-reported experience in infectious disease modelling or a related field) showed similar performance, both on the natural (WIS two weeks ahead: 43k for experts vs. 43k for non-experts for cases, 41 vs. 46 for deaths) and the log scale (0.24 vs. 0.26 for cases, 0.16 vs. 0.13 for deaths, see Figure \ref{fig:performance-experts}) and Table \ref{tab:scores-expert}. Precise results changed depending on whether or not direct forecasts, $R_t$ forecasts or both were scored.

% As a direct comparison of individual scores between "experts" and "non-experts" is biased by missing forecasts,

@@

Just like \citet{bosseComparingHumanModelbased2022} and \citet{farrowHumanJudgmentApproach2017}, this study struggled to retain a large number of participants. Focused public outreach efforts such as creating a dedicated website, announcing an official tournament, providing a public leaderboard, sending weekly emails with details on past performance and weekly announcements on Twitter, did noticeably increase participation compared to the previous study in Germany and Poland. Nevertheless, retaining participants beyond the initial recruitment proved challenging, and most forecasters only submitted a single forecast. \citet{mcandrewChimericForecastingCombining2022} had a higher number of participants, suggesting that making use of existing forecasting platforms, such as Metaculus or Good Judgement Open that provide access to a large existing user base may be helpful in recruiting a larger number of participants though these lack the flexibility and software tooling to run a novel study of this kind in real-time as things stand.

>>>>

The median number of unique participants in any given week was 17, the minimum was 6 and the maximum was 51. This was higher than the number of participants in \cite{bosseComparingHumanModelbased2022} (which had a median number of 6, a minimum of 2, and a maximum 10). With respect to the number of submissions from an individual participant, we observed similar patterns as \cite{bosseComparingHumanModelbased2022}: An individual forecaster participated on average in 2.6 weeks out of 13. The median number of submissions from a single individual was one, meaning that similar to \citep{bosseComparingHumanModelbased2022} most forecasters dropped out after their first submission. Only five participants submitted a forecast in ten or more weeks and only two submitted a forecast in all thirteen weeks, one of whom is an author on this study. The number of direct forecasts (median: 13 for cases and 12 for deaths) was higher than the number of $R_t$ forecasts (median: 6 for both cases and deaths) in all weeks (see Figure \ref{fig:num-forecasters}). The median number of "non-experts" (11 for cases, 10 for deaths) was higher than the median number of "experts" (8 for cases and deaths).

@@

%Mention calbration

% Mention number of experts and non-experts

An median ensemble of two week ahead forecasts made only by "experts" or "non-experts" (determined based on self-reported experience in infectious disease modelling or a related field) performed worse than the combined crowd example, both for cases and deaths and both on the log scale and on the natural scale (see Figure \ref{fig:performance-experts} and Table \ref{tab:scores-experts}).

For cases two week ahead, "experts" achieved better scores than "non-experts" both on the log and on the natural scale. WIS values \textit{relative to the combined crowd ensemble} were 1.08 for "experts" and 1.14 for "non-experts" on the log scale and 1.06 for "experts" and 1.07 for "non-experts" on the natural scale (see Table \ref{tab:scores-experts}).

For two week ahead forecasts of deaths, "experts" performed worse than "non-experts" in terms of WIS on the log scale (WIS relative to the combined crowd ensemble: 1.29 vs. 1.06), but better on the natural scale (1.03 vs. 1.14).

For four weeks ahead forecasts of cases, the combined ensemble outperformed both "experts" and "non-experts" on the log scale as well as on the natural scale. "Experts" performed better than "non-experts" both on the log scale (1.08 for "experts" vs. 1.21 for "non-experts") and on the natural scale (1.04 vs. 1.07). For four week ahead forecasts of deaths, "Experts" performed better than "Non-experts" on the log scale (1.17 vs. 1.18) as well as on the natural scale (0.95 vs. 1.15).

@@

Just like \citet{bosseComparingHumanModelbased2022} and \citet{farrowHumanJudgmentApproach2017}, this study struggled to retain a large number of participants. Focused public outreach efforts such as creating a dedicated website, announcing an official tournament, providing a public leaderboard, sending weekly emails with details on past performance and weekly announcements on Twitter, did noticeably increase participation compared to the previous study in Germany and Poland. Nevertheless, retaining participants beyond the initial recruitment proved challenging, and most forecasters only submitted a single forecast. \citet{mcandrewChimericForecastingCombining2022} had a higher number of participants, suggesting that making use of existing forecasting platforms, such as Metaculus or Good Judgement Open that access to a large existing user base and greater resources may be helpful in recruiting a larger number of participants though these lack the flexibility and software tooling to run a novel study of this kind in real-time as things stand.
